Comparing vector-based and Bayesian memory models using large-scale datasets:\protect\\User-generated hashtag and tag prediction on Twitter and StackOverflow

### 2016-06-16 writeups/psycMethodsResponse2/response.tex

% http://tex.stackexchange.com/questions/36423/random-unwanted-space-between-paragraphs
\raggedbottom

\begin{document}

To Lisa	Harlow and Fred	Oswald,	co-editors, \bigskip

Please see below our responses to the comments.
Along with pasting text from the revised document inline with the questions where applicable,
I have also attached a version of the .pdf that contains markup for the differences between the original and revised submission. \bigskip

We hope that you find these changes sufficient and that you find the revised document well suited for this special issue. \bigskip

@@

-Clayton Stanley

\bigskip
\bigskip

\begin{questions}

\question Primary concern: Papers on predictive modeling typically avoid confidence intervals and instead seek to optimize out-of-sample RMSE or R2 based on training versus test samples (e.g., k-fold cross-validation) or sometimes by resampling (bootstrapping); see overviews of predictive modeling such as http://www-bcf.usc.edu/~gareth/ISL/ and http://appliedpredictivemodeling.com/.  The general concern here is that people reading your paper alongside other 'big data' papers may view your confidence interval approach unusual or outdated; the more specific concern here is overfitting the model to the data (making confidence intervals too confident).

\begin{solution}
Added a paragraph in the Overall Method section to address this concern.
The text is included below:

FIXME: add text

@@

\begin{solution}
The work presented in this paper was done for my dissertation.
The dissertation paper is available from Rice University's digital archive (https://scholarship.rice.edu/handle/1911/88165).
\end{solution}

Reviewer 3:

\question The counterintuitive results are also intriguing (such as the finding that larger training corpora lowered performance for the random permutations models). However, one factor to consider is that RP models depend on the approximate orthogonality of the random projections (the environment vectors for Beagle). As the number of words increases, this will tend to oversaturate the space, and commonly leads to decreased performance. One standard approach here is to scale the dimensionality of the representations as the training set and vocabulary sizes increase. It would be interesting to see if the performance still leveled off if you increased the dimensionality with the corpus size.

\begin{solution}
Addressed this by including in the paper the work that looked at model accuracy versus corpus size and number of rows in the random permutation model.
The text for the section has been previously included in this document.
\end{solution}

### 2016-06-16 writeups/psycMethods/psycMethods.tex
foo

Other successful models have shown that higher-level processes such as a user's goals for picking a hashtag, demographics, and specifics about how a hashtag has been used in the past can also influence hashtag use.
\textcite{lin2013bigbirds} showed that there are at least two distinct use cases for hashtags on Twitter: to mark the content (traditional tagging) and to contribute to a specific community that has created a hashtag.
\textcite{yang2012we} found that demographics such as gender, age, and location can influence a user's selected hashtag.
\textcite{denton2015user} found that the growth and lifetime of a hashtag can be influenced by factors such as how often the hashtag was retweeted and the number of followers for a user that used a particular hashtag.
These types of goal-related features, demographic information, and higher-level attributes of previous hashtag use were not directly included in the declarative memory models that were tested for this research.
They were not included because it would be difficult to fit these features into a modeling framework that is constrained to use only declarative memory processes,
and this research focused on measuring differences in model accuracy for two declarative memory models.
Nonetheless many of these higher-level features may indirectly influence a declarative memory model by influencing the specific tags that a user has chosen in the past,
which in turn boosts base-level activation for these previously-chosen tags, which in turn makes it more likely that they are chosen in the future.

>>>>

Other successful models have shown that higher-level processes such as a user's goals for picking a hashtag, demographics, and specifics about how a hashtag has been used in the past can also influence hashtag use.
\textcite{lin2013bigbirds} showed that there are at least two distinct use cases for hashtags on Twitter: to mark the content (traditional tagging) and to contribute to a specific community that has created a hashtag.
\textcite{yang2012we} found that demographics such as gender, age, and location can influence a user's selected hashtag.
\textcite{denton2015user} found that the growth and lifetime of a hashtag can be influenced by factors such as how often the hashtag was retweeted and the number of followers for a user that used a particular hashtag.
These types of goal-related features, demographic information, and higher-level attributes of previous hashtag use were not directly included in the declarative memory models that were tested for this research.
They were not included because it would be difficult to fit these features into a modeling framework that is constrained to use only declarative memory processes,
and this research focused on measuring differences in model accuracy for two declarative memory models.
Nonetheless, many of these higher-level features may indirectly influence a declarative memory model by influencing the specific tags that a user has chosen in the past,
which in turn boosts base-level activation for these previously-chosen tags, which in turn makes it more likely that they are chosen in the future.
